Quantifying the global film festival circuit: networks, diversity and value creation

### 2023-02-19 cudan/paperplots.qmd
gender

sixgcols = c(divergingx_hcl(6, palette="Zissou 1") %>% {.[6]=darken(.[6],0.3);.},  "gray50") 
sixcols = c(divergingx_hcl(6, palette="Zissou 1") %>% {.[6]=darken(.[6],0.3);.}, "gray10",  "gray50") 
langcols= c(divergingx_hcl(6, palette="Zissou 1")%>% {.[6]=darken(.[6],0.3);.}, "gray10",  "gray50")[c(1,3,5,6,7,8)]

@@

divyearplot = function(vecs, ex, shape=16, yl="", splitab=T, convert=T, networkstats=T){
  if(splitab){
    vecs = vecs %>% mutate(YearEvent=case_when(ab=="A"~YearEvent-0.15,
                                               ab=="B"~YearEvent+0.15 )) %>% 
      arrange(libelleFestival_NEW_VZ) %>% 
      mutate(series = substr(libelleFestival_NEW_VZ, 1,15))
    if(length(unique(vecs$libelleFestival_NEW_VZ)) != 
       length(unique(vecs$series))){ stop("shortening mismatch")}
    g=ggplot(vecs , 
        aes(YearEvent, target, color=ab, shape=ab,  text=tool))
  } else {
     vex = vecs %>% 
       filter(libelleFestival_NEW_VZ %in% ex) %>% 
       mutate(libelleFestival_NEW_VZ=fct_relevel(libelleFestival_NEW_VZ, ex))
     g=ggplot(vex , 
        aes(YearEvent, target, color=ab, shape=ab,  text=tool))
  }

@@

  if(!splitab & !is.null(ex)){
   if(networkstats){
      fromy=2014.5; toy=2019.5
    } else{
      fromy=2008; toy=2022
      g=g+geom_errorbar(aes(ymin=lower, ymax=upper), color="gray40", width=0.1, size=0.45)
    }
    g=
      g+facet_wrap(~libelleFestival_NEW_VZ, nrow = length(ex)/6)+
      # geom_point( aes(YearEvent, target),data=vecs %>% select(-libelleFestival_NEW_VZ), inherit.aes = F,
      #             color="gray90", size=0.9)+
      geom_line(data=vex %>% filter(YearEvent>fromy, YearEvent<toy) %>% 
                  group_by(YearEvent, libelleFestival_NEW_VZ) %>% 
                  summarise(target=mean(target, na.rm=T), tool=NA, ab=ab[1]), 
                color="gray60", size=0.3
                )+
      geom_point(data=vex, alpha=1, size=1.5, shape=16)+
      scale_x_continuous(breaks=seq(2009,2021,3) )+
      scale_y_continuous(limits=c( min(vecs$target), max(vecs$target) ))+
      theme(
       panel.grid.major.x  = element_line(color="gray95"),
       panel.grid.minor.x  = element_blank(),
       legend.position = 'none'
       )
  }
  if(convert){

    ggplotly(g,tooltip="text") %>% config(doubleClickDelay=500)
  } else {g}

@@

gg=function(g){
  ggplotly(g, tooltip="text") %>%  config(doubleClickDelay=500)
}

@@

>>>>

sixgcols = c(divergingx_hcl(6, palette="Zissou 1") %>% {.[6]=darken(.[6],0.3);.},  "gray50") %>%
  {.[1]=lighten(.[1],0.4);.} %>% 
  desaturate(0.07) %>% {.[c(2)]=darken(.[c(2)],0.1);.} 
sixcols = c(divergingx_hcl(6, palette="Zissou 1") %>% {.[c(1)]=darken(.[c(1)],0.3);.}, "gray10",  "gray50") 
langcols= c(divergingx_hcl(6, palette="Zissou 1")%>% {.[c(1)]=darken(.[c(1)],0.3);.}, "gray10",  "gray50")[c(1,3,5,6,7,8)] 
rolecols=divergingx_hcl(31, palette="Zissou 1")  %>% {c(.[1:2], "gray75", .[30:31])}

@@

divyearplot = function(vecs, ex, shape=16, yl="", splitab=T, convert=T, networkstats=T, ylims=NULL){
  if(splitab){
    vecs = vecs %>% mutate(YearEvent=case_when(ab=="A"~YearEvent-0.15,
                                               ab=="B"~YearEvent+0.15 )) %>% 
      arrange(libelleFestival_NEW_VZ) %>% 
      mutate(series = substr(libelleFestival_NEW_VZ, 1,15))
    if(length(unique(vecs$libelleFestival_NEW_VZ)) != 
       length(unique(vecs$series))){ stop("shortening mismatch")}
    g=ggplot(vecs , 
        aes(YearEvent, target, color=ab, shape=ab,  text=tool))
  } else {
     vex = vecs %>% 
       filter(libelleFestival_NEW_VZ %in% ex) %>% 
       mutate(libelleFestival_NEW_VZ=fct_relevel(libelleFestival_NEW_VZ, ex))
     g=ggplot(vex , 
        aes(YearEvent, target, color=ab, shape=ab,  text=tool))
  }

@@

  if(!splitab & !is.null(ex)){
   if(networkstats){
      fromy=2014.5; toy=2019.5
    } else{
      fromy=2008; toy=2022
      g=g+geom_errorbar(aes(ymin=lower, ymax=upper), color="gray40", width=0.1, size=0.45)
    }
    g=
      g+facet_wrap(~libelleFestival_NEW_VZ, nrow = length(ex)/6)+
      # geom_point( aes(YearEvent, target),data=vecs %>% select(-libelleFestival_NEW_VZ), inherit.aes = F,
      #             color="gray90", size=0.9)+
      geom_line(data=vex %>% filter(YearEvent>fromy, YearEvent<toy) %>% 
                  group_by(YearEvent, libelleFestival_NEW_VZ) %>% 
                  summarise(target=mean(target, na.rm=T), tool=NA, ab=ab[1]), 
                color="gray60", size=0.3
                )+
      geom_point(data=vex, alpha=1, size=1.5, shape=16)+
      scale_x_continuous(breaks=seq(2009,2021,3) )+
      scale_y_continuous(limits=c( min(vecs$target), max(vecs$target) ))+
      theme(
       panel.grid.major.x  = element_line(color="gray95"),
       panel.grid.minor.x  = element_blank(),
       legend.position = 'none'
       )
  }

  if(!is.null(ylims)){
    g=g+scale_y_continuous(limits = ylims)
  }

  if(convert){

    return( ggplotly(g,tooltip="text") %>% plotly::config(doubleClickDelay=500) 
            )
  } else {
    return(g+theme(legend.position = "none"))
           }

@@

gg=function(g){
  ggplotly(g, tooltip="text") %>%  plotly::config(doubleClickDelay=500)
}

@@

# * Gender diversity

Using producer and director first name gender, where identifiable, to calculate ratio in a film; festivals are means of film ratios.

```{r}
cat(attr(festrolevecs, "info"))
```

g=ggplot(festrolevecs, mapping=aes(ratiopf, ratiodf, color=ratiof, shape=ab, size=ab, text=tool))+
  geom_vline(xintercept = 0.5)+
  geom_hline(yintercept = 0.5)+
  geom_point()+
  scale_size_manual(values =c(1.4,0.8)*1.2, guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype")+
  scale_color_gradientn(colours =rolecols, name="Female\nto male\nratio\namong\nproducers\n&directors", limits=c(0,1))+
  theme_bw()+
  theme(#legend.position = 'none',
        plot.background = element_rect( fill="white")
  )+
  labs(x="Producers", y="Directors")
  NULL

if(convertplots){
  gg(g)
} else {g}

```
(the cross is 50-50 lines)

```{r}
divyearplot(festrolevecs  %>% mutate(target=ratiof),ex=NULL, yl="Average % of female producers & directors", convert=T, networkstats = F, ylims=c(0,1))

divyearplot(festrolevecs  %>% mutate(target=ratiof, lower=ratiofmin, upper=ratiofmax),
            ex=exgenfests, yl="Female to male ratio", convert=convertplots, splitab=F, networkstats = F, ylims=c(0,1))

Note the intervals are different here, being the min-max calculated based on the number of unknown/unidentifiable/unisex first names among directors and producers in a given festival. They are not the same as the 95% bootstrapped confidence intervals, and therefore less conservative.
